Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-17 paper.tex
conclusion draft

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{imgs/coverage-test.pdf}
    \caption{Coverage in the three types of scenarios}
    \label{fig:coverage-test}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{imgs/inside-test}
    \caption{Number of agents inside the phenomenon in the three types of scenarios}
    \label{fig:inside-test}
  \end{subfigure}
  \begin{subfigure}[b]{0.85\linewidth}
    \includegraphics[width=\linewidth]{imgs/inside-two-test}
    \caption{Two zones scenario: agent inside each phenomenon}
    \label{fig:inside-two-test}
  \end{subfigure}
  \begin{subfigure}[b]{0.85\linewidth}
    \includegraphics[width=\linewidth]{imgs/coverage-two-test}
    \caption{Two zones scenario: coverage of each area}
    \label{fig:coverage-two-test}
  \end{subfigure} 
  \caption{Quantative test results in the three types of scenarios.
  We can see that the proposed approach is able to cover and track the phenomenon better than the baselines.
  }
  \label{fig:test}
\end{figure*}
\section{Conclusion and Future Work}
\ga{Page budget: 0.5}
\label{sec:conclusion}

>>>>

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{imgs/coverage-test.pdf}
    \caption{Coverage in the three types of scenarios}
    \label{fig:coverage-test}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{imgs/inside-test}
    \caption{Number of agents inside the phenomenon in the three types of scenarios}
    \label{fig:inside-test}
  \end{subfigure}
  \begin{subfigure}[b]{0.85\linewidth}
    \includegraphics[width=\linewidth]{imgs/inside-two-test}
    \caption{Two zones scenario: agent inside each phenomenon}
    \label{fig:inside-two-test}
  \end{subfigure}
  \begin{subfigure}[b]{0.85\linewidth}
    \includegraphics[width=\linewidth]{imgs/coverage-two-test}
    \caption{Two zones scenario: coverage of each area}
    \label{fig:coverage-two-test}
  \end{subfigure} 
  \caption{Quantative test results in the three types of scenarios.
  We can see that the proposed approach is able to cover and track the phenomenon better than the baselines.
  }
  \label{fig:test}
\end{figure*}
\section{Conclusion and Future Work}
In this paper, 
 we have introduced a novel approach for constructing distributed controllers by leveraging aggregate computing to encode agent interactions, 
 along with the combination of \ac{DQN} and \ac{GNN} for synthesizing distributed intelligence.
The proposed \emph{Field-Informed reinforcement learning} approach offers a promising solution to the challenges faced in coordinating multi-agent systems. 
By combining manual design and machine learning techniques, 
 the approach enables agents to autonomously learn and adapt their behaviour while leveraging locally available information. 
%
The demonstrated success in the proposed case study in solving collective tasks underscores the potential impact of this approach in advancing the field of multi-agent systems and swarm robotics.

Future research could explore its application in diverse domains and evaluate its scalability and robustness in increasingly complex scenarios. 
%
In addition, we also plan to take the approach to modern actor-critical solutions, which are better suited to modern swarm robotics problems because of the continuous action space.
\ga{Page budget: 0.5}
\label{sec:conclusion}
